---
title: "Monopoly Test"
output: html_document
---
#METHODS
To begin the game of Monopoly, we must incorporate the rules of the game. Creating the board, dice, community chest cards, chance cards, and players were all needed. Vectors were used to create the board and both card sets. A function was created to incorporate the rules within the dice themselves, such as doubles and no doubles, resulting in another turn for the player or switching turns. For creating the players, the setRefClass function was needed for the creation of fields and methods that are associated with and referenced by the specific player. Multiple methods were nested within this function, including updating position of the players, jail functions, and rolling doubles functions. Functions for the chance deck and community chest were created to move and interact with the players when landed on. Lastly, there was a function needed to initiate and switch players' turns throughout the game.

---
title: "STAT 345 Final Project - Real Estate"
author: "STAT 345 - Braden Barglind, Adam Steckbauer, Stephen Koch, Douglas Klister"
output: html_document
---

Expected Submission: You will generate a well-written R Markdown report that addresses the following prompts. This R Markdown report should source your analysis code and only display top-level, abstracted code _if/when appropriate_. Choices made during the analysis project should be described and justified in the report. You will present on your results during the final exam period for the semester. The written report (knitted file), presentation file, and your analysis code should be submitted to D2L by Tuesday, May 14 at 12:15pm. 

**General advice:** Get started early. If you wait to the last minute, it will not go well. For this project, you may find yourself spending a reasonable amount of time _searching_ for help.

1. _Rules!_ Monopoly has several rules related to movement around the game board. Movement is affected by standard dice rolls, special conditions for some dice rolls, and game cards. Find and summarize these rules. 

2. _Let's Get Moving_ Build a system that allows for up to 4 players to move around the game board. As a first attempt, focus on standard dice rolls, ignoring additional rules related to rolling doubles, jail, or special cards. Which properties are landed on most frequently? Create a visualization for this!

3. _Double Down_ Improve your system to incorporate going to jail, including the doubles-rolling condition. Which properties are landed on most frequently now? Has this changed dramatically from the previous system (that didn't account for jail)? Again, visualize this!

4. _Take a Chance_ Incorporate the movement cards into your system. You can ignore the effects of non-movement cards, but not their existence! Which properties are landed on most frequently now? Has this changed dramatically from the previous system (that didn't account for Chance)? Again, visualize this!

5. _Play a Game_ Extend your system to allow for up to 4 players to "play" the game. You may choose a reasonable starting board and player money level (so, you don't have to buy properties). Include payments between players, payments to the bank, and payments from the bank (there are several cards that will effect these that you should account for). You do not need to consider mortgaging properties (so a player loses when their liquid cash has run out). How long do games typically last given your starting board and money level? How does this change if money paid to the bank is placed in "Free Parking" and awarded to players landing on that space?

******************
```{r}
#Libraries
library(tidyverse)
library(jtools)
```

```{r}
#Monopoly Board Vector
monopoly_board <- data.frame(space = 1:40, title = c("Go", "Mediterranean Avenue", "Community Chest 1", "Baltic Avenue", "Income Tax", "Reading Railroad", "Oriental Avenue", "Chance 1", "Vermont Avenue", "Connecticut Avenue", "Jail", "St. Charles Place", "Electric Company", "States Avenue", "Virginia Avenue", "Pennsylvania Railroad", "St. James Place", "Community Chest 2", "Tennessee Avenue", "New York Avenue", "Free Parking", "Kentucky Avenue", "Chance 2", "Indiana Avenue", "Illinois Avenue", "B. & O. Railroad", "Atlantic Avenue", "Ventnor Avenue", "Water Works", "Marvin Gardens", "Go to Jail", "Pacific Avenue", "North Carolina Avenue", "Community Chest 3", "Pennsylvania Avenue", "Short Line", "Chance 3", "Park Place", "Luxury Tax", "Boardwalk"), stringsAsFactors = FALSE)
```

```{r}
#Chance Cards Vector
chance_cards <- data.frame(index = 1:16, card = c("Advance to Go", "Advance to Illinois Ave - If you pass Go, collect $200", "Advance to St. Charles Place – If you pass Go, collect $200", "Advance token to nearest Utility. If unowned, you may buy it from the Bank. If owned, throw dice and pay owner a total ten times the amount thrown.", "Advance token to the nearest Railroad and pay owner twice the rental to which he/she {he} is otherwise entitled. If Railroad is unowned, you may buy it from the Bank.", "Bank pays you dividend of $50", "Get Out of Jail Free", "Go Back 3 Spaces", "Go to Jail–Go directly to Jail–Do not pass Go, do not collect $200", "Make general repairs on all your property–For each house pay $25–For each hotel $100", "Pay poor tax of $15", "Take a trip to Reading Railroad–If you pass Go, collect $200", "Take a walk on the Boardwalk–Advance token to Boardwalk", "You have been elected Chairman of the Board–Pay each player $50", "Your building and loan matures—Collect $150", "You have won a crossword competition—Collect $100"))
```
 
 
```{r}
#Community Chest Cards Vector
community_cards <-  data.frame(index = 1:17, card = c("Advance to Go", "Bank error in your favor", "Doctor's fee", "From sale of stock you get $50", "Get Out of Jail Free", "Go to Jail", "Grand Opera Night", "Holiday Fund matures", "Income tax refund", "It is your birthday", "Life insurance matures", "Pay hospital fees", "Pay school fees", "Recieve consultancy fee", "You are assessed for street repairs", "You have won second prize in a beauty", "You inherit $100"))
```

```{r}
#Creating the Dice Rolls
#dice has no arguements
#dice outputs: faces - two random numbers between 1 and 6 (two ints)
#              doubles - if doubles were rolled (TRUE or FALSE)
#              movement - the total of the two randomly generated numbers between 1 and 6 (int)

dice <- function(){
  faces <- sample(1:6,2, replace = TRUE)
  if(faces[1] == faces[2]) doubles = TRUE
  else doubles = FALSE
  movement = sum(faces)
  return(list(faces=faces, doubles=doubles, movement=movement))
}
```


```{r}
#Creating the Players
#the setRefClass function allows for the creation of fields (similar to variables) and methods (similar to functions) that are associated with and referenced by the specific player
# the fields (variables) created for the player inlcude: pos - used to track the position of the player
#                                                        jail - tracks if the player is in jail and if they are how many turns they have been in jail
#                                                        rolldouble - tracks how many doubles have been rolled in a row, if exceeds three, the player is sent to jail
# the methods (functions) created for each player include: move_n - used to add the new roll(s) of the player to the positon to find where the player currently is
#                                                          go_to_space_n - used to update the position of the player
#                                                          increase_jail - adds one to jail when the player is placed in jail or the player fails to roll doubles when in jail
#                                                          reset_jail - resets the variable jail when the player gets out of jail
#                                                          increase_double - adds one to the variable double when doubles are rolled
#                                                          reset_double - resets the amount of doubles rolled in a row to 0 when the player does not roll doubles

player <- setRefClass("player", fields = list(
  #positon of player on the board
  pos="numeric", 
  
  #if 0, player is not in jail, if greater than 0, represents amount of turns player has been in jail
  jail = "numeric",
  
  # amount of doubles player has rolled in a row
  rolldouble = "numeric"
  ), 
method = list(
#moves player by "n" positions and if pos is greater than 40, restarts player at beginning of game board
move_n = function(n){
#adds n which is found by roll of dice to position
pos <<- pos + n
#if position if greater than 40, subtracts 40 to start player at beginning of gameboard
if(pos > 40) pos <<- pos - 40
return(pos)}, 

#sends player to specifc position
go_to_space_n = function(n){
#sets the position of the player to n
pos <<-  n
},

#adds on to jail
increase_jail = function(){
  jail <<- jail + 1
},

#resets jail to 0
reset_jail = function(){
  jail <<- 0
    },

# increases doubles by 1 if doubles are rolled
increase_double = function(){
  rolldouble <<- rolldouble + 1
    },

#resets doubles to 0 if doubles are not rolled
reset_double = function(){
  rolldouble <<- 0
    },
#Sends the player to the jail space  
 go_to_jail = function(){
  pos <<- 11
}
 
    
 }
```


```{r}
#Function for the Chance Deck
#called when a player lands on one of the three chance positions
#takes two arguments: player and tracking
#no output but updates the players positons and the tally of the amount of times each positions have been landed on if neccessary
#not all chance cards are taken into account since some are too complicated for this simulation

drawchance <- function(player, tracking) {
#draw finds a number between one and fifteen which represents a specifc chance card by using the sample function
draw <- sample(1:15, 1)

#if the draw is between one and nine, there is movement associated with the chance card which access the if statement
if (draw %in% 1:9) {
  #tracking is increased to record the position which the player has landed on
  tracking$increase_count(player$pos)
  
  #the next 20 lines of code determine which specifc chance card was drawn and how the player is moved based on the chance card drawn
  #based on the card drawn, the go_to_space_n, go_to_jail, or move_n function is accessed
  #if the card drawn is 4 or 5 the current positon is aksed and based on the player's current postion they are moved to a new position
  if (draw == 1){
    player$go_to_space_n(1) }
  if (draw == 2){
    player$go_to_space_n(25) }
  if (draw == 3){
    player$go_to_space_n(12) }
  if (draw == 4){
    if (player$pos == 8){
      player$go_to_space_n(13) }
    if (player$pos == 23){
      player$go_to_space_n(29) }
    if (player$pos == 37){
      player$go_to_space_n(5) }
  }
  if (draw == 5){
    if (player$pos == 8){
      player$go_to_space_n(16) }
    if (player$pos == 23){
      player$go_to_space_n(26) }
    if (player$pos == 37){
      player$go_to_space_n(6) }
  }
  if (draw == 6){
    player$go_to_space_n(6) }
  if (draw == 7){
    player$go_to_space_n(40) }
  if (draw == 8){
    player$go_to_jail() }
  if (draw == 9){
    player$move_n(-3) }
} }
```


```{r}
#Function for the Community Chest Deck
#called when a player lands on one of the three community chest positions
#takes two arguments: player and tracking
#no output but updates the players positons and the tally of the amount of times each positions have been landed on if neccessary
#not all community chest cards are taken into account since some are too complicated for this simulation

community_function <- function(player, tracking) {
#draw finds a number between one and sixteen which represents a specifc chance card by using the sample function
draw <- sample(1:16, 1)

#if the dar is either 1 or 2 the player moves thier position
if (draw %in% 1:2) {
  #the tracking is updated based on the position that the player orignally landed on
  tracking$increase_count(player$pos) }

#if one is drawn the player is sent too the "Go" position
if (draw == 1){
  player$go_to_space_n(1) }
  
#if two is drawn the player is sent too the "Jail" position
if (draw == 2){
  player$go_to_jail() }
}
```


```{r}
#Tracking the Player's Movements
#the setRefClass function allows for the creation of fields (similar to variables) and methods (similar to functions) that are associated with and referenced by the specific player
# the field (variable) include tally - used to keep track of the amount of times each position has been landed on
# the methods (functions) include increase_count - used to increase the tally when a player lands on a new position
tracking <- setRefClass("tracking",
    fields = list(
      #tally is a list of amounts of times each positon has been landed on
      tally = "numeric"
), 
    methods = list(
      #increase_count adds one when each specifc position is landed on by indexing the specifc postions
      increase_count = function(n){
        tally[n] <<- tally[n] + 1
        } 
    ) 
)
```

```{r}
#Initiates Player's Turns with only movement
#plays each players turns without doubles or card movement 
#takes two arguments: player and tracking
#no output but calls functions to update the player's positon and the tally of the amount of times each positions have been landed on

basicturn <- function(player, tracking) {
  #roll the dice and give the output to roll
  roll <- dice()
  
  #move the player the required spaces 
  player$move_n(roll$movement)
  
  #move the player and record the space landed on
  tracking$increase_count(player$pos)
}
```

```{r}
#Initiates the Players' Turns with movement, doubles and jail
# plays out each player's turn now with jail and doubles
#takes two arguments: player and tracking
#no output but calls functions to update the player's positon and the tally of the amount of times each positions have been landed on

doublesturn <- function(player, tracking) {
  #roll is set to the number produced by the function dice
roll <- dice()

#value of doubles (TRUE or FLASE) is set to go_again
go_again <- roll$doubles

# if the doubles id true and player's variable "Jail" is greater than one the player gets out of jail
if (roll$doubles & player$jail) {
#jail is reset to 0
player$reset_jail()

#player moves n positions from the jail based on a new roll
player$move_n(roll$movement)

#doubles are reset to 0
roll$reset_double()

#go_again is set to FLASE to stop player
go_again <- FALSE

#if player rolls doubles and is not in jail, doubles increase until they are sent to jail or fail to roll doubles
} else if(roll$doubles & !player$jail) {

#increase_double is called for the specifc player
player$increase_double()

#if player rolled 3 doubles in a row, the player is sent to jail
if (roll$doubles == 3){
#go to jail and reset double function is called
player$go_to_jail()
roll$reset_double()
#go_again is set to FLASE to stop the player from going
go_again <- FALSE

} else {
#if double is not at 3, the player continues to roll and play
player$move_n(roll$movement)

} } else if ( !roll$doubles & player$jail) {
#get out of jail if 3rd turn in jail

if (player$jail == 3){
#the variable jail ie equal to 3, the player automatically escapes from jail
#the move_n and reset_jail functions are called to set jail to 0 and move the player by n positions
player$move_n(roll$movement)
player$reset_jail()

} else {
# if jail is less than 3, the increase_jail function is called to record that the player has spent a turn in jail
player$increase_jail()

} } else if ( !roll$doubles & !player$jail){
#if the player fails to roll doubles and is not in jail, the player moves using the move_n function and resets their doubles 
#this chucnk runs for most "usual" situations
player$move_n(roll$movement)
roll$reset_double
}

#if player isn't on "go to jail" spot
if (player$pos != 31) {
#Tracking keeps track of the amount of occurences each position is landed on
tracking$increase_count(player$pos)

if (go_again){
#if go_again is TRUE the player would continue their turn
taketurn(player, tracking)

} } else {
#tally go to jail, then go to jail and tally location
tracking$increase_count(player$pos)
player$go_to_jail()
tracking$increase_count(player$pos)
}

}
```

```{r}
#Initiates Players' Turns
#take turn plays each players turn by calling other applicable functions 
#takes two arguments: player and tracking
#no output but calls functions to update the player's positon and the tally of the amount of times each positions have been landed on

taketurn <- function(player, tracking) {
#roll is set to the number produced by the function dice
roll <- dice()

#value of doubles (TRUE or FLASE) is set to go_again
go_again <- roll$doubles

# if the doubles id true and player's variable "Jail" is greater than one the player gets out of jail
if (roll$doubles & player$jail) {
#jail is reset to 0
player$reset_jail()

#player moves n positions from the jail based on a new roll
player$move_n(roll$movement)

#doubles are reset to 0
roll$reset_double()

#go_again is set to FLASE to stop player
go_again <- FALSE

#if player rolls doubles and is not in jail, doubles increase until they are sent to jail or fail to roll doubles
} else if(roll$doubles & !player$jail) {

#increase_double is called for the specifc player
player$increase_double()

#if player rolled 3 doubles in a row, the player is sent to jail
if (roll$doubles == 3){
#go to jail and reset double function is called
player$go_to_jail()
roll$reset_double()
#go_again is set to FLASE to stop the player from going
go_again <- FALSE

} else {
#if double is not at 3, the player continues to roll and play
player$move_n(roll$movement)

} } else if ( !roll$doubles & player$jail) {
#get out of jail if 3rd turn in jail

if (player$jail == 3){
#the variable jail ie equal to 3, the player automatically escapes from jail
#the move_n and reset_jail functions are called to set jail to 0 and move the player by n positions
player$move_n(roll$movement)
player$reset_jail()

} else {
# if jail is less than 3, the increase_jail function is called to record that the player has spent a turn in jail
player$increase_jail()

} } else if ( !roll$doubles & !player$jail){
#if the player fails to roll doubles and is not in jail, the player moves using the move_n function and resets their doubles 
#this chucnk runs for most "usual" situations
player$move_n(roll$movement)
roll$reset_double
}

#draw chance card
if (player$pos %in% c(8,23,37)){
drawchance(player, tracking)

#the the player is sent to jail, go_again is FALSE and they do no get "Go" money
if (player$jail){
go_again <- FALSE
} }

#draw community chest card 
if(player$pos %in% c(3, 18, 34)){
community_function(player,tracking)
  
#the the player is sent to jail, go_again is FALSE and they do no get "Go" money  
if(player$jail) {
  go_again <- FALSE
}}

#if player isn't on "go to jail" spot
if (player$pos != 31) {
#Tracking keeps track of the amount of occurences each position is landed on
tracking$increase_count(player$pos)

if (go_again){
#if go_again is TRUE the player would continue their turn
taketurn(player, tracking)

} } else {
#tally go to jail, then go to jail and tally location
tracking$increase_count(player$pos)
player$go_to_jail()
tracking$increase_count(player$pos)
}}
```

```{r}
#Set seed for Unique Simulation
set.seed(12345)
```

```{r}
#Running simulation based on basic movement

#space tracking keeps track of how many times each location has been visited
space_tracking <- tracking$new(tally = rep(0,40))
#Simulating game with 4 players. Simulate 1000 times to ensure a large enough sample and accuracy of the means. Each player has 30 turns in a game on average, according to Google. 

#each player is initialized with three fields pos, jail, and roll double set to values for starting the game
for(i in 1:1000){
  player1 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player2 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player3 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player4 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  
  #basic turn function is called with inputs of the specifc player and space tracking
  for(i in 1:30){
    basicturn(player1, space_tracking)
    basicturn(player2, space_tracking)
    basicturn(player3, space_tracking)
    basicturn(player4, space_tracking)
  }
}


#adding the tally of how many times each property was landed on in the simulation to the dataframe monopoly board
basic_turn_results <- cbind(monopoly_board, tally = space_tracking$tally)
#adding the proportion of times each property was landed on in the simulation to the dataframe
basic_turn_results <- cbind(basic_turn_results, rel = basic_turn_results$tally/sum(basic_turn_results$tally))


#presenting the results from most likely to be landed on to least likely
head(arrange(basic_turn_results, desc(rel)))
```

```{r}
basic_turn_results$title <- factor(basic_turn_results$title,levels = monopoly_board$title )
ggplot(data = basic_turn_results, aes(x = reorder(title, -tally), y = tally)) + geom_bar(stat = "Identity")  + scale_fill_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Space Tallies with Basic Movement", x = "Space", y = "Times Landed On") + theme(axis.text.x = element_text(angle = 90))
```


```{r}
#Now running simulation with added jail and doubles rules (doublesturn)
set.seed(12345)

space_tracking <- tracking$new(tally = rep(0,40))

#each player is initialized with three fields pos, jail, and roll double set to values for starting the game
for(i in 1:1000){
  player1 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player2 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player3 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player4 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  
  #doubles turn function is called with inputs of the specific player and space tracking
  for(i in 1:30){
    doublesturn(player1, space_tracking)
    doublesturn(player2, space_tracking)
    doublesturn(player3, space_tracking)
    doublesturn(player4, space_tracking)
  }
}


#adding the tally of how many times each property was landed on in the simulation to the dataframe monopoly board
doubles_turn_results <- cbind(monopoly_board, tally = space_tracking$tally)
#adding the proportion of times each property was landed on in the simulation to the dataframe
doubles_turn_results <- cbind(doubles_turn_results, rel = doubles_turn_results$tally/sum(doubles_turn_results$tally))


#presenting the results from most likely to be landed on to least likely
head(arrange(doubles_turn_results, desc(rel)))
```

```{r}
doubles_turn_results$title <- factor(doubles_turn_results$title,levels = monopoly_board$title )
ggplot(data = doubles_turn_results, aes(x = reorder(title, -tally), y = tally)) + geom_bar(stat = "Identity")  + scale_fill_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Space Tallies with Basic Movement + Doubles and Jail", x = "Space", y = "Times Landed On") + theme(axis.text.x = element_text(angle = 90))
```

```{r}
#Now running simulation with added jail, doubles and cards rules (taketurn)
set.seed(12345)

space_tracking <- tracking$new(tally = rep(0,40))


#each player is initialized with three fields pos, jail, and roll double set to values for starting the game
for(i in 1:1000){
  player1 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player2 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player3 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  player4 <- player$new(pos = 1, jail = 0, rolldouble = 0)
  
  #take turn function is called with inputs of the specific player and space tracking
  for(i in 1:30){
    taketurn(player1, space_tracking)
    taketurn(player2, space_tracking)
    taketurn(player3, space_tracking)
    taketurn(player4, space_tracking)
  }
}


#adding the tally of how many times each property was landed on in the simulation to the dataframe monopoly board
results <- cbind(monopoly_board, tally = space_tracking$tally)
#adding the proportion of times each property was landed on in the simulation to the dataframe
results <- cbind(results, rel = results$tally/sum(results$tally))


#presenting the results from most likely to be landed on to least likely
head(arrange(results, desc(rel)))
```

```{r}
results$title <- factor(results$title,levels = monopoly_board$title )
ggplot(data = results, aes(x = reorder(title, -tally), y = tally)) + geom_bar(stat = "Identity")  + scale_fill_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Space Tallies with Basic Movement + Doubles and Jail + Cards", x = "Space", y = "Times Landed On") + theme(axis.text.x = element_text(angle = 90))
```
How did the Three Different simulations change the results? Well, with basic movement, all the spaces are visited in relatively even amounts. There will be some differences based on how there are two dice rolled at once, and the players all start at the same spot, but overall the numbers are close.

When you add the rules for doubles and jail, then the number of times the Jail is visited increases a lot. Part of that is due to how every turn you end at the Jail, the tally is increased, so when you stay in jail rolling for doubles, you increase the count of the Jail Space. This also gives extra space tallies to properties around the jail area because you get moved over there often by cards and rolling doubles. 

Finally, when you add the rules for Drawing Cards, you still see the large number of Jail Tallies, but now you also see large numbers for places you can get moved to by drawing a chance or community chest card. Places like Illinois Avenue, Reading Railroad and GO have larger numbers than others because of this. 


Now we start to analyze the data from the simulation that implemented doubles, jail and cards


This first code chunk sets up the factors needed for analysis. The expected_payment vectors are the probability that the space was landed on multiplied by the rent charged. This gives an expected income for each property each turn based on long run numbers. The cost_total vectors add the cost of the property to the cost of added houses and hotels. Finally, the expected_turns_to_repay vectors give the expected number of turns it would take to repay the investment (cost of property and buildings) 

```{r, message=FALSE}
prop_data <- tibble(read.csv("monopolypropertydata.csv"))


m_data <- inner_join(results, prop_data, by = "space")
just_prop <- m_data %>% drop_na(Hotel)

just_prop <- just_prop %>% mutate(expected_payment_base = rel*No_House_Doubled, expected_payment_one_house = rel*One_House, expected_payment_two_houses = rel*Two_Houses, expected_payment_three_houses = rel*Three_Houses, expected_payment_four_houses = rel*Four_Houses, expected_payment_hotel = rel*Hotel)

just_prop <- just_prop %>% mutate(hotel_cost_total = 5* House_Cost + Sale_Cost, four_houses_cost_total = 4* House_Cost + Sale_Cost, three_houses_cost_total = 3* House_Cost + Sale_Cost, two_houses_cost_total = 2* House_Cost + Sale_Cost, one_house_cost_total =  House_Cost + Sale_Cost)

just_prop <- just_prop %>% mutate(expected_turns_to_repay_hotel = hotel_cost_total/expected_payment_hotel, expected_turns_to_repay_four_houses = four_houses_cost_total/expected_payment_four_houses, expected_turns_to_repay_three_houses = three_houses_cost_total/ expected_payment_three_houses, expected_turns_to_repay_two_houses = two_houses_cost_total/expected_payment_two_houses, expected_turns_to_repay_one_house = one_house_cost_total/expected_payment_one_house, expected_turns_to_repay_base = Sale_Cost/expected_payment_base)
```

Now the first graph I will start out with the the cost of property vs the expected payment per turn with no houses. In this case, the numbers are doubled because it is assumed that you own the whole color set for each because we will be comparing this to property with investments. In this first graph You can see some winners and some losers in base form. Boardwalk is an obvious outlier based on the very high rent, but the cost really makes park place suffer because of how it does not share the same high rent.The first three sets are pretty average and follow the fit line, but the red and orange sets are slightly above and the Yellow and Green are slightly below. 

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = Sale_Cost, y = expected_payment_base, size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black")+ scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Cost of Property vs Expected Payment per turn No Houses", x = "Cost of Property", y = "Expected Payment per turn")
```
Now lets look at the final potential for these properties. We can see how the first set falls off in expected payment and now the light blue set is below the fit line. Once you get into the middle of the board, the Pink, Orange and Red sets are above the line. Not much has changed for the Yellow and Green sets though, as they are slightly lower in expected payment. The final Blue set still has the large difference between the 350 dollar Park Place and 400 Dollar Boardwalk. 

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = Sale_Cost, y = expected_payment_hotel, size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black")+ scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Cost of Property vs Expected Payment per turn With Hotels", x = "Cost of Property", y = "Expected Payment per turn")
```

This next Graph adds in the cost of houses, which increase by 50 dollars each as you travel along the sides of the square board. The first two sets have 50 dollar houses while the last two have 200 dollar houses. You can see this as the sets are grouped by two because of the house costs. You can see how this really looks good for the orange set, the second set for 100 dollar houses sets, but the sheer amount of times Illinois avenue is landed on really helps its numbers. Another interesting sight is the Green set. It suffers from the 200 dollar houses and weak rent.

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = hotel_cost_total, y = expected_payment_hotel,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() +labs(title = "Total Cost of Hotel and Property vs Expected Payment per Turn with Hotels", x = "Total Cost of Hotel and Property", y = "Expected Payment per Turn with Hotels")

```

To get a better look at things, we will start to look at expected turns to break even (make back all the money you spend on the property). Notice the Outliers at the ends: Boardwalk, Park Place and especially Mediterranean Avenue. The following six graphs will go through the expected turns to break even through all stages of development

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = Sale_Cost, y = expected_turns_to_repay_base,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Cost of Property vs Expected Turns to Break Even With No Houses", x = "Cost of Property", y = "Expected Turns to Break Even With No Houses")
```

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = one_house_cost_total, y = expected_turns_to_repay_one_house,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Total Cost vs Expected Turns to Break Even With One House", x = "Total Cost of Property and One House", y = "Expected Turns to Break Even With One House")
```

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = two_houses_cost_total, y = expected_turns_to_repay_two_houses,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Total Cost vs Expected Turns to Break Even With Two Houses", x = "Total Cost of Property and Two Houses", y = "Expected Turns to Break Even With Two Houses")
```

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = three_houses_cost_total, y = expected_turns_to_repay_three_houses,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Total Cost vs Expected Turns to Break Even With Three Houses", x = "Total Cost of Property and Three Houses", y = "Expected Turns to Break Even With Three Houses")
```

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = four_houses_cost_total, y = expected_turns_to_repay_four_houses,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Total Cost vs Expected Turns to Break Even With Four Houses", x = "Total Cost of Property and Four Houses", y = "Expected Turns to Break Even With Four Houses")
```

```{r, message=FALSE}
ggplot(data = just_prop, aes(x = hotel_cost_total, y = expected_turns_to_repay_hotel,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Total Cost vs Expected Turns to Break Even With Hotels (Five Houses)", x = "Total Cost of Property and Hotel", y = "Expected Turns to Break Even With Hotels")
```
There are a couple of trends I would like to point out. The first major point is Mediterranean Avenue. Why is it so different from the fit line? There are two reasons for this. First, its location right next to start does it no favors because at the start of the game and if you ever land on or get sent to start, it is impossible to move one space with two dice, so it gets landed on very infrequently. Second, it has the same cost as the other property in the brown set, but has rent values that are almost half! The hotel rent for Mediterranean Avenue is 250 dollars compared to the rent cost of 450 for Baltic (the other property in the brown set). 

The second interesting trend I would like to look at is the Expected turns to break even as you increase investment. Rent values are so low in the beginning that a property with investment will have a quicker time to break even. This is the game telling you to invest in property in order to bankrupt your opponents. 

The third trend I would like to address is the slope of the fit line. It increases as you add development. This means that with no houses, the more expensive properties have smaller expected number of turns to break even than less expensive properties. However, when you start increasing development, the advantage sways towards the less expensive properties, as now they take less turns to break even. 


The next graph is an average of the expected turns to break even across the different levels of development. This gives a general idea of how quickly the properties repay their investments over the investment process. This graph shows how sets 2 through 5 are some of the best options compared to the rest of the sets. You can also see how the first set has really poor value because of Mediterranean Avenue and how there is a plateau in break even turns around 100 with the last few sets if you don't count Boardwalk.

```{r, message=FALSE}
just_prop <- just_prop %>% mutate(mean_turns_to_break_even = (expected_turns_to_repay_base + expected_turns_to_repay_one_house + expected_turns_to_repay_two_houses + expected_turns_to_repay_three_houses + expected_turns_to_repay_four_houses + expected_turns_to_repay_hotel) / 6 )

ggplot(data = just_prop, aes(x = Sale_Cost, y = mean_turns_to_break_even,  size = 2)) + geom_point(aes(color = Identifier)) + geom_smooth(method = lm, se = FALSE, size =1, color = "black") + scale_color_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Cost of Property vs Mean Turns to Break Even", x = "Cost of Property", y = "Mean Turns to Break Even")
```

This vector shows the top 6 properties in terms of a fast return on investment.The one thing you may notice three of them are the Orange set, and they are right after Boardwalk, which has a massive Hotel rent and Illinois Ave, which is the most landed on property. 

```{r}
head(just_prop %>% select(space, title, Identifier, Sale_Cost, mean_turns_to_break_even) %>% arrange(mean_turns_to_break_even))
```

```{r}
color_tbe <- just_prop %>% select(space, title, Identifier, Sale_Cost, mean_turns_to_break_even) %>% group_by(Identifier) %>% summarize(color_mean_turns_to_break_even = mean(mean_turns_to_break_even)) %>% arrange(color_mean_turns_to_break_even)
color_tbe
```

```{r}
color_tbe$Identifier <- factor(color_tbe$Identifier,levels = c("Blue", "Brown", "Green", "Light Blue", "Orange", "Pink", "Red", "Yellow"))
ggplot(data = color_tbe, aes(x = reorder(Identifier, color_mean_turns_to_break_even), y = color_mean_turns_to_break_even)) + geom_bar(stat = "Identity", aes(fill = Identifier))  + scale_fill_manual(values = c("blue","brown", "green3", "light blue", "orange", "purple", "red","yellow3")) + theme_bw() + labs(title = "Cost of Property vs Mean Turns to Break Even", x = "Set Color", y = "Mean Turns to Break Even for the Set")
```
Here the mean turns to break even averaged through the set. This shows the best overall sets for quick break even point and the arithmetic average gives strong weight to the larger hotel rent numbers, so you will also have high rents to really hit your opponents with a high bill in the late game. As you can see, orange, blue and red are the strongest sets from our simulation. Pink and Yellow are not much farther behind, but Green, is starting to take quite a while to make back your investment, and Light Blue and Brown may only be good in the short term if a bunch of people get unlucky and land on them while you have invested in them. 

Conclusion:

